---
title: "surrogate_working"
author: "Victor Møller"
date: "21 nov 2018"
output: html_document
---

Two things are needed: 
--> making the long-form dataframe (eventually d14)
--> making the surrogate pairs (eventually expand)

Making the long-form dataframe.
This could be more "tidy" or clean. 
But, we can work on that later perhaps. 

```{r}
d5 <- d4 %>%
  mutate(group2 = ifelse(group == 10, 2, group)) #This works because 2 comes after (just like 10 does. So, it works by accident - which is good enough for now.)

d5$group2 <- as.factor(d5$group2)

#it works. 
table(d5$group2)
summary(d5$group2)
summary(d5$group) #5890 both - so it is good. 


#Subset for melting with RESP
d6 <- d5 %>%
  ungroup() %>%
  select(resp1S, resp2S, group2)

d7 <- melt(d6, id.vars = "group2")

#Subset for melting with HR
d8 <- d5 %>%
  ungroup() %>%
  select(hr1S, hr2S, group2)

d9 <- melt(d8, id.vars = "group2")

#Renaming both d7 & d9 
d7 <- d7 %>%
  rename(resp = variable, resp_value = value)

d9 <- d9 %>%
  rename(hr = variable, hr_value = value)

#combining & eliminating 
d10 <- cbind(d7, d9)
d10 <- d10[,-4] #getting rid of one of the group2 columns. 

#Adding a unique column 
library(tidyr)
d11 <- d10 %>%
  mutate(greatness = paste(group2, resp))

d11$greatness <- as.factor(as.numeric(as.factor(d11$greatness)))
summary(d11$greatness) #great stuff. 

#adding something more 
#doing something 
d12 <- d5 %>%
  ungroup() %>%
  select(hr1S, hr2S, condition)

d13 <- melt(d12, id.vars = "condition")

d14 <- cbind(d11, d13)
d14 <- d14[,-c(8:9)]
d14$greatness <- as.numeric(d14$greatness)
```

Expand 

```{r setup, include=FALSE}
#Making the pairs 
set.seed(666)
expand <- expand.grid(persons1 = seq(1,18,1), persons2 = seq(1,18,1)) %>%
  filter(persons1 < persons2)
  
#153 combinations. 
expand <- expand %>%
  rename(p1 = persons1, p2 = persons2) 

```

The actual function

```{r cars}
n = 1
# conversation
surrogate_func_c <- function(data) {
  
  #create an empty df
  df <- data.frame()
  df <- setNames(data.frame(matrix(ncol=11, nrow=153)),c('p1','p2',"RR_resp","DET_resp","NRLINE_resp","maxL_resp","L_resp","ENTR_resp", "rENTR_resp", "LAM_resp", "TT_resp"))
  
  for (n in 1:153) {
    # participants
    p1 <- dplyr::filter(data, greatness == expand[n,1] , condition == "Conversation") 
    p2 <- dplyr::filter(data, greatness == expand[n,2] , condition == "Conversation")
    
    #vectors 
    v1 <- p1$resp_value
    v2 <- p2$resp_value
      
    #run crqa
    results <- crqa(v1, v2, embed = 2, delay = 25.5, radius = 0.408, normalize = 0,  rescale = 0,  mindiagline = 2,  minvertline = 2,  tw = 0,  whiteline = FALSE,  recpt = FALSE)
    
    # save into a df
    df$p1[n] <- unique(p1$greatness)
    df$p2[n] <- unique(p2$greatness)
    df$RR_resp[n] <- results$RR
    df$DET_resp[n] <- results$DET
    df$NRLINE_resp[n] <- results$NRLINE
    df$maxL_resp[n] <- results$maxL
    df$L_resp[n] <- results$L
    df$ENTR_resp[n] <- results$ENTR
    df$rENTR_resp[n] <- results$rENTR
    df$LAM_resp[n] <- results$LAM
    df$TT_resp[n] <- results$TT
    
    n = n+1
  }
  return(df)    
  }

fuckme <- surrogate_func_c(d14)
```

And fuckme is the beautiful end product of a messy process. 
Note: we still have to run functions for the other 2 conditions, but we should probably 
be content with just doing three different functions at this point (only takes a miniscule change in the code)

