---
title: "A4_P1_function"
author: "JK"
date: "8 listopadu 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(pacman)
p_load(tidyverse,
       gridExtra, #grid.arrange()
       crqa, #crqa()
       lmerTest,
       doParallel, #parallel processing
       reshape2,
       Hmisc, #errorbars in plotting
       groupdata2) #downsampling

# parallel processing
cl <- makeCluster(detectCores(), type='PSOCK')
registerDoParallel(cl)
```

```{r loading finished stuff}
# preprocessed data
d4 <- read_csv("d4.csv")


# optimal parameters
med_optimal_para <- read_csv("med_optimal_para.csv")


# crqa datasets
crqa_real <- read_csv("crqa_real.csv") %>%
  mutate(reality_status = "real") %>%
  mutate_all(funs(replace(., is.na(.), 0)))

crqa_shuff <- read_csv("crqa_shuff.csv") %>%
  mutate(reality_status = "shuffled") %>%
  mutate_all(funs(replace(., is.na(.), 0)))

crqa_surr <- read_csv("crqa_surr.csv") %>%
  mutate(reality_status = "surrogate") %>%
  mutate_all(funs(replace(., is.na(.), 0))) %>%
  mutate(p1 = ifelse(p1 == 0, NA, p1),
         p2 = ifelse(p2 == 0, NA, p2))

# merging
crqa_results <- full_join(crqa_real, crqa_shuff) %>%
  full_join(crqa_surr)
 
  
```


## data plotto
```{r plotting}
plotty <- function(data, group_nr){
  c1 <- data %>%
    filter(group == group_nr) %>%
    ggplot() +
    geom_line(aes(as.numeric(TimeMs.x), hr1S, color = "P1")) +
    geom_line(aes(as.numeric(TimeMs.x), hr2S, color = "P2")) +
    labs(x = "time in 100 ms", y = "HR") +
    theme(legend.position="bottom")
  
  # scaled RESP
  c2 <- data %>%
    filter(group == group_nr) %>%
    ggplot() +
    geom_line(aes(as.numeric(TimeMs.x), resp1S, color = "P1")) +
    geom_line(aes(as.numeric(TimeMs.x), resp2S, color = "P2")) +
    labs(x = "time in 100 ms", y = "RESP") +
    theme(legend.position="bottom")
  
  ## colected
  grid.arrange(c1, c2, ncol=2, top = "Plots of physiological data (HR, RESP, ECG) with downsampling, outlier removal & scaling", 
               bottom = paste0("Group ", group_nr))
  
}

plotty(d4, group_nr = "2")
```

### RP plotting
```{r}
RP=results_test$RP
RP = matrix(as.numeric(RP), nrow = ncol(RP))
cols = c("white", "blue4")
image(RP, xlab = "", ylab = "", col = cols)

Profile=drpdfromts(test$resp1S, test$resp2S,datatype = 'continuous',ws=50,radius=1.68739078850316)
timecourse = round( seq(-5000,5000,100)/1000, digit = 1)
mindip = Profile$mindip/1000
profile = Profile$profile*100
Prof=data.frame(profile)
ggplot(Prof, aes(timecourse,profile))+geom_line()+ geom_vline(xintercept = timecourse[mindip], colour='red')
```



# MODELING
## scale variables
```{r scaling}
# new df not to overwrite
crqa_scaled <- crqa_results

# MINMAX
for (i in c(1:9)) {
  minc = min(crqa_scaled[,i])
  maxc = max(crqa_scaled[,i])
  crqa_scaled[,i] = (crqa_scaled[,i]-minc)/(maxc-minc)
}

# keep it clean
rm(i, maxc, minc)
```

## subsetting

```{r model subset}
#subsets for modelling 
crqa_HR <- crqa_scaled %>%
  filter(metric == "hr1S")

crqa_RESP <- crqa_scaled %>%
  filter(metric == "resp1S")
```


```{r first modeling}
#RR based on reality status  
m1 <- lm(RR ~ condition * reality_status, crqa_RESP) 

m2 <- lm(RR ~ condition * reality_status, crqa_HR)
summary(m2)


#DET based on reality status
m3 <- lm(DET ~ condition * reality_status, crqa_RESP)
summary(m3)

m4 <- lm(DET ~ condition * reality_status, crqa_HR)
summary(m4)

#predicting heart coordination from respiration coordination
df_list <- split(crqa_results, crqa_results$metric)
crqa_split <- do.call("cbind", df_list)

m5 <- lm(hr1S.RR ~ resp1S.RR, crqa_split)
summary(m5)

m6 <- lm(hr1S.DET ~ resp1S.DET, crqa_split)
summary(m6)

m7 <- lm(hr1S.L ~ resp1S.L, crqa_split)
summary(m7)
```

## for quick summary
```{r bullshit summary function}
predictors <- names(crqa_real)[1:9]
all_cals <- paste0(predictors, " ~ condition * reality_status")

model_summary <- function(call, data) {
  
  model <- lm(call, data)
  
  model_df <- model %>%
    summary() %>%
    broom::tidy() %>%
    mutate(model = as.character(call))
  
  return(model_df)
}

summary_hr <- map_df(all_cals,
                     model_summary,
                     crqa_HR)

summary_resp <- map_df(all_cals,
                       model_summary,
                       crqa_RESP)
```


# plotting the interactions

Apparent issues:
--> all zeroes for shuffled for most parameters. 

Things that make sense:
--> Errorbars are smaller for surrogate comp. w. real (because of more obs.)
--> Never a significant difference between real & surrogate bc. of huge errorbars of real. 

Different effects plotted:
--> RR
--> DET
--> maxL

```{r interaction plot}

#RR for HR
ggplot(crqa_HR, aes(condition, RR, color = reality_status, group = reality_status)) +
  stat_summary(fun.y = mean, geom = "point", size = 1) + 
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar") +
  stat_summary(fun.y = mean, geom = "line") +
  labs(title ="HR")

#RR for RESP
ggplot(crqa_RESP, aes(condition, RR, color = reality_status, group = reality_status)) +
  stat_summary(fun.y = mean, geom = "point", size = 1) + 
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar") +
  stat_summary(fun.y = mean, geom = "line") +
  labs(title = "RESP")

#DET for HR
ggplot(crqa_RESP, aes(condition, DET, color = reality_status, group = reality_status)) +
  stat_summary(fun.y = mean, geom = "point", size = 1) + 
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar") +
  stat_summary(fun.y = mean, geom = "line") +
  labs(title = "RESP")

#DET for RESP
ggplot(crqa_RESP, aes(condition, DET, color = reality_status, group = reality_status)) +
  stat_summary(fun.y = mean, geom = "point", size = 1) + 
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar") +
  stat_summary(fun.y = mean, geom = "line") +
  labs(title = "RESP")

#maxL for HR 
ggplot(crqa_HR, aes(condition, maxL, color = reality_status, group = reality_status)) +
  stat_summary(fun.y = mean, geom = "point", size = 1) + 
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar") +
  stat_summary(fun.y = mean, geom = "line") +
  labs(title = "RESP")

#maxL for RESP
ggplot(crqa_RESP, aes(condition, maxL, color = reality_status, group = reality_status)) +
  stat_summary(fun.y = mean, geom = "point", size = 2) + 
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", size = 0.8) +
  stat_summary(fun.y = mean, geom = "line", size = 0.8) +
  labs(title = "RESP")

```

Can heart rate coordination be predicted by respiration coordination?
Spoiler: as of now (there are some issues with the approach sketched) no. 
This is intended as a simplified example of the pipeline of predicting. 
Probably one has to make folds & do cross-validation. 

```{r}

library(tidyverse)
## getting rid of shuffle because it is shit 
crqa_split_noshuf <- crqa_split %>%
  filter(resp1S.reality_status != "shuffled")


## 75% of the sample size
smp_size <- floor(0.75 * nrow(crqa_split_noshuf))

## set the seed to make your partition reproducible
set.seed(123)
train_ind <- sample(seq_len(nrow(crqa_split_noshuf)), size = smp_size)

## the above is not taking into account that we would like the diff. conditions / baselines to be equal in training and test - so this is just sample code. 

train <- crqa_split_noshuf[train_ind, ]
test <- crqa_split_noshuf[-train_ind, ]

## Building models 
library(pacman)
p_load(tidyverse, lme4)

## rescaling should be done. 
model1 = lm(hr1S.DET ~ resp1S.RR + resp1S.DET + resp1S.NRLINE + resp1S.maxL + resp1S.L + resp1S.ENTR + resp1S.rENTR + resp1S.LAM + resp1S.TT + (1|resp1S.condition) + (1|resp1S.reality_status),  data = train, REML = FALSE)
summary(model1)

## prediction 
test$pred <- predict(model1, test, allow.new.levels = TRUE)

## predictions visualized 
ggplot(test, aes(hr1S.DET, pred), color = ) +
  geom_point() +
  geom_smooth()

#### cross-validation would be better ####

```

