---
title: "A4_P1_function"
author: "JK"
date: "8 listopadu 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(pacman)
p_load(tidyverse,
       gridExtra, #grid.arrange()
       egg,
       crqa, #crqa()
       lmerTest,
       doParallel, #parallel processing
       reshape2,
       merTools, #predictInterval
       Hmisc, #errorbars in plotting
       groupdata2) #downsampling

# parallel processing
cl <- makeCluster(detectCores(), type='PSOCK')
registerDoParallel(cl)
```

```{r loading finished stuff}
# preprocessed data
d4 <- read_csv("d4.csv")


# optimal parameters
med_optimal_para <- read_csv("med_optimal_para.csv")


# crqa datasets
crqa_real <- read_csv("crqa_real.csv") %>%
  mutate(reality_status = "real") %>%
  mutate_all(funs(replace(., is.na(.), 0)))

crqa_shuff <- read_csv("crqa_shuff.csv") %>%
  mutate(reality_status = "shuffled") %>%
  mutate_all(funs(replace(., is.na(.), 0)))

crqa_surr <- read_csv("crqa_surr.csv") %>%
  mutate(reality_status = "surrogate") %>%
  mutate_all(funs(replace(., is.na(.), 0))) %>%
  mutate(p1 = ifelse(p1 == 0, NA, p1),
         p2 = ifelse(p2 == 0, NA, p2))

# merging
crqa_results <- full_join(crqa_real, crqa_shuff) %>%
  full_join(crqa_surr)
 
  
```


## data plotto
```{r plotting}
plotty <- function(data, group_nr){
  c1 <- data %>%
    filter(group == group_nr) %>%
    ggplot() +
    geom_line(aes(as.numeric(TimeMs.x), hr1S, color = "P1")) +
    geom_line(aes(as.numeric(TimeMs.x), hr2S, color = "P2")) +
    labs(x = "time in 100 ms", y = "HR") +
    theme(legend.position="bottom")
  
  # scaled RESP
  c2 <- data %>%
    filter(group == group_nr) %>%
    ggplot() +
    geom_line(aes(as.numeric(TimeMs.x), resp1S, color = "P1")) +
    geom_line(aes(as.numeric(TimeMs.x), resp2S, color = "P2")) +
    labs(x = "time in 100 ms", y = "RESP") +
    theme(legend.position="bottom")
  
  ## colected
  grid.arrange(c1, c2, ncol=2, top = "Plots of physiological data (HR, RESP, ECG) with downsampling, outlier removal & scaling", 
               bottom = paste0("Group ", group_nr))
  
}

plotty(d4, group_nr = "2")
```

# RP plotting
## CRQA function
```{r}
crqa_RP_HR <- function(df, group_nr_cond) {
  
  # filtering argument
  filtering_args <- data.frame(whack = group_nr_cond) %>%
    separate(whack, c("cond", "group_nr"), sep = "_")
  
  cond <- filtering_args$cond
  group_nr <- filtering_args$group_nr
  
  # filtering
  data <- df %>%
    dplyr::filter(condition == as.character(cond)) %>%
    dplyr::filter(group ==as.numeric(group_nr))
    
  
  # computing
  crqa_list <- crqa(ts1 = data[["hr1S"]], 
                            ts2 = data[["hr2S"]], 
                            delay = 10, #delay 
                            embed = 16, #emdim 
                            radius = 1.4586380, #radius
                            normalize = 0,
                            rescale = 0,
                            mindiagline = 2,
                            minvertline = 2)

  return(crqa_list)
}

crqa_RP_RESP <- function(df, group_nr_cond) {
  
  # filtering argument
  filtering_args <- data.frame(whack = group_nr_cond) %>%
    separate(whack, c("cond", "group_nr"), sep = "_")
  
  cond <- filtering_args$cond
  group_nr <- filtering_args$group_nr
  
  # filtering
  data <- df %>%
    dplyr::filter(condition == as.character(cond)) %>%
    dplyr::filter(group ==as.numeric(group_nr))
    
  
  # computing
  crqa_list <- crqa(ts1 = data[["resp1S"]], 
                            ts2 = data[["resp2S"]], 
                            delay = 22.5, #delay 
                            embed = 2, #emdim 
                            radius = 0.4078281, #radius
                            normalize = 0,
                            rescale = 0,
                            mindiagline = 2,
                            minvertline = 2)

  return(crqa_list)
}
```

## group with highest RR 
Group 4 has the highest average RR of respiration
All heartrate RR is similarly bad. Therefore, group 4 will be used for demonstration
```{r}
avg_rr <- crqa_real %>%
  group_by(group, metric) %>%
  summarise(meanRR = mean(RR),
            meanmaxL = mean(maxL),
            meanL = mean(L))
```

## getting RP plots
```{r}
hr4sy <- crqa_RP_HR(d4, "Synchronous_4")$RP
hr4co <- crqa_RP_HR(d4, "Conversation_4")$RP
hr4tt <- crqa_RP_HR(d4, "TurnTaking_4")$RP

resp4sy <- crqa_RP_RESP(d4, "Synchronous_4")$RP
resp4co <- crqa_RP_RESP(d4, "Conversation_4")$RP
resp4tt <- crqa_RP_RESP(d4, "TurnTaking_4")$RP
```

OLD DON'T RUN
```{r}
## MATRIX
hr4sy_m = matrix(as.numeric(hr4sy), nrow = ncol(hr4sy))
hr4co_m = matrix(as.numeric(hr4co), nrow = ncol(hr4co))
hr4tt_m = matrix(as.numeric(hr4tt), nrow = ncol(hr4tt))

resp4sy_m = matrix(as.numeric(resp4sy), nrow = ncol(resp4sy))
resp4co_m = matrix(as.numeric(resp4co), nrow = ncol(resp4co))
resp4tt_m = matrix(as.numeric(resp4tt), nrow = ncol(resp4tt))


## COLORS
cols = c("white", "black")
par(pty = "s")


## PLOTS
### HR PLOTS
image(hr4sy_m, main = "HR, Synchronous", sub = "Group 4", 
      xlab = "", ylab = "", col = cols)

image(hr4co_m, main = "HR, Conversation", sub = "Group 4", 
      xlab = "", ylab = "", col = cols)

image(hr4tt_m, main = "HR, Turn Taking", sub = "Group 4", 
      xlab = "", ylab = "", col = cols)


### RESP IMAGES

image(resp4sy_m, main = "RESP, Synchronous", sub = "Group 4", 
      xlab = "", ylab = "", col = cols)

image(resp4co_m, main = "RESP, Conversation", sub = "Group 4", 
      xlab = "", ylab = "", col = cols)

image(resp4tt_m, main = "RESP, Turn Taking", sub = "Group 4", 
      xlab = "", ylab = "", col = cols)

```

TRASH BIN
```{r} 
# RP=results_test$RP
# RP = matrix(as.numeric(RP), nrow = ncol(RP))
# cols = c("white", "blue4")
# image(RP, xlab = "", ylab = "", col = cols)
# 
# Profile=drpdfromts(test$resp1S, test$resp2S,datatype = 'continuous',ws=50,radius=1.68739078850316)
# timecourse = round( seq(-5000,5000,100)/1000, digit = 1)
# mindip = Profile$mindip/1000
# profile = Profile$profile*100
# Prof=data.frame(profile)
# ggplot(Prof, aes(timecourse,profile))+geom_line()+ geom_vline(xintercept = timecourse[mindip], colour='red')
```



# MODELING
## scale variables
```{r scaling}
# new df not to overwrite
crqa_scaled <- crqa_results

# MINMAX
for (i in c(1:9)) {
  minc = min(crqa_scaled[,i])
  maxc = max(crqa_scaled[,i])
  crqa_scaled[,i] = (crqa_scaled[,i]-minc)/(maxc-minc)
}

# keep it clean
rm(i, maxc, minc)
```

## subsetting

```{r model subset}
#subsets for modelling 
crqa_HR <- crqa_scaled %>%
  filter(metric == "hr1S")

crqa_RESP <- crqa_scaled %>%
  filter(metric == "resp1S")
```


```{r first modeling}
#RR based on reality status  
m1 <- lm(RR ~ condition * reality_status, crqa_RESP) 

m2 <- lm(RR ~ condition * reality_status, crqa_HR)
summary(m2)


#DET based on reality status
m3 <- lm(DET ~ condition * reality_status, crqa_RESP)
summary(m3)

m4 <- lm(DET ~ condition * reality_status, crqa_HR)
summary(m4)

#predicting heart coordination from respiration coordination
df_list <- split(crqa_results, crqa_results$metric)
crqa_split <- do.call("cbind", df_list)

m5 <- lm(hr1S.RR ~ resp1S.RR, crqa_split)
summary(m5)

m6 <- lm(hr1S.DET ~ resp1S.DET, crqa_split)
summary(m6)

m7 <- lm(hr1S.L ~ resp1S.L, crqa_split)
summary(m7)
```

## for quick summary
```{r bullshit summary function}
predictors <- names(crqa_real)[1:9]
all_cals <- paste0(predictors, " ~ condition * reality_status")

model_summary <- function(call, data) {
  
  model <- lm(call, data)
  
  model_df <- model %>%
    summary() %>%
    broom::tidy() %>%
    mutate(model = as.character(call))
  
  return(model_df)
}

summary_hr <- map_df(all_cals,
                     model_summary,
                     crqa_HR)

summary_resp <- map_df(all_cals,
                       model_summary,
                       crqa_RESP)
```


# plotting the interactions

Apparent issues:
--> all zeroes for shuffled for most parameters. 

Things that make sense:
--> Errorbars are smaller for surrogate comp. w. real (because of more obs.)
--> Never a significant difference between real & surrogate bc. of huge errorbars of real. 

Different effects plotted:
--> RR
--> DET
--> maxL

```{r}
# input data
reality_status <- as.factor(c(rep("real", 3), 
                              rep("shuffled", 3), 
                              rep("surrogate", 3)))

condition <- as.factor(rep(c("Conversation", "Synchronous", "TurnTaking"), 3))

input_det <- data.frame(reality_status, condition)


# output data
predicted_det <- cbind(input_det ,predict(m3, input_det, interval = 'confidence'))
```


```{r interaction plot}

#RR for HR
ggplot(crqa_HR, aes(condition, RR, color = reality_status, group = reality_status)) +
  stat_summary(fun.y = mean, geom = "point", size = 1) + 
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar") +
  stat_summary(fun.y = mean, geom = "line") +
  labs(title ="HR")

#RR for RESP
ggplot(crqa_RESP, aes(condition, RR, color = reality_status, group = reality_status)) +
  stat_summary(fun.y = mean, geom = "point", size = 1) + 
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar") +
  stat_summary(fun.y = mean, geom = "line") +
  labs(title = "RESP")

#DET for HR
ggplot(crqa_RESP, aes(condition, DET, color = reality_status, group = reality_status)) +
  stat_summary(fun.y = mean, geom = "point", size = 1) + 
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar") +
  stat_summary(fun.y = mean, geom = "line") +
  labs(title = "RESP")

#DET for RESP
### REAL DATA
observed_resp_plot <- crqa_RESP %>%
  filter(reality_status != "shuffled") %>%
  ggplot(aes(condition, DET, color = reality_status, group = reality_status)) +
  stat_summary(fun.y = mean, geom = "point", size = 2) + 
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.5) +
  stat_summary(fun.y = mean, geom = "line") +
  ylim(c(0.7, 0.9)) +
  labs(title = "RESP observed data", subtitle = "\nmin-max scaled, with 95% CI") +
  #guides(color=FALSE) +
  theme_bw()

### MODEL
model_resp_plot <- predicted_det %>%
  filter(reality_status != "shuffled") %>%
  ggplot(aes(condition, fit, color = reality_status, group = reality_status)) +
  stat_summary(fun.y = mean, geom = "point", size = 2) + 
  geom_errorbar(aes(ymin = lwr, ymax = upr), width = 0.5) +
  stat_summary(fun.y = mean, geom = "line") +
  ylim(c(0.7, 0.9)) +
  labs(title = "RESP model mean predictions", 
       subtitle = "DET ~ condition * reality_satus \nmin-max scaled, with 95% CI of fitted value",
       y = "fitted DET") +
  #guides(color=FALSE) +
  theme_bw()

### WITHOUT EXCLUDING SHUFFLED
observed_bogus <- crqa_RESP %>%
  ggplot(aes(condition, DET, color = reality_status, group = reality_status)) +
  stat_summary(fun.y = mean, geom = "point", size = 2) + 
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.5) +
  stat_summary(fun.y = mean, geom = "line") +
  ylim(c(0, 0.9)) +
  labs(title = "RESP observed data", subtitle = "\nmin-max scaled, with 95% CI") +
  #guides(color=FALSE) +
  theme_bw()

model_bogus <- predicted_det %>%
  ggplot(aes(condition, fit, color = reality_status, group = reality_status)) +
  stat_summary(fun.y = mean, geom = "point", size = 2) + 
  geom_errorbar(aes(ymin = lwr, ymax = upr), width = 0.5) +
  stat_summary(fun.y = mean, geom = "line") +
  ylim(c(0, 0.9)) +
  labs(title = "RESP model mean predictions", 
       subtitle = "DET ~ condition * reality_satus \nmin-max scaled, with 95% CI of fitted value",
       y = "fitted DET") +
  #guides(color=FALSE) +
  theme_bw()

#maxL for HR 
ggplot(crqa_HR, aes(condition, maxL, color = reality_status, group = reality_status)) +
  stat_summary(fun.y = mean, geom = "point", size = 1) + 
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar") +
  stat_summary(fun.y = mean, geom = "line") +
  labs(title = "RESP")

#maxL for RESP
ggplot(crqa_RESP, aes(condition, maxL, color = reality_status, group = reality_status)) +
  stat_summary(fun.y = mean, geom = "point", size = 2) + 
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", size = 0.8) +
  stat_summary(fun.y = mean, geom = "line", size = 0.8) +
  labs(title = "RESP")

```

## grid.arrange
```{r}
grid_arrange_shared_legend <-
  function(...,
           ncol = length(list(...)),
           nrow = 1,
           position = c("bottom", "right")) {
    
    plots <- list(...)
    position <- match.arg(position)
    g <-
      ggplotGrob(plots[[1]] + theme(legend.position = position))$grobs
    legend <- g[[which(sapply(g, function(x)
      x$name) == "guide-box")]]
    lheight <- sum(legend$height)
    lwidth <- sum(legend$width)
    gl <- lapply(plots, function(x)
      x + theme(legend.position = "none"))
    gl <- c(gl, ncol = ncol, nrow = nrow)
    
    combined <- switch(
      position,
      "bottom" = arrangeGrob(
        do.call(arrangeGrob, gl),
        legend,
        ncol = 1,
        heights = unit.c(unit(1, "npc") - lheight, lheight)
      ),
      "right" = arrangeGrob(
        do.call(arrangeGrob, gl),
        legend,
        ncol = 2,
        widths = unit.c(unit(1, "npc") - lwidth, lwidth)
      )
    )
    
    grid.newpage()
    grid.draw(combined)
    
    # return gtable invisibly
    invisible(combined)
    
  }

grid_arrange_shared_legend(observed_resp_plot, model_resp_plot)

grid_arrange_shared_legend(observed_bogus, model_bogus)

```


Can heart rate coordination be predicted by respiration coordination?
Spoiler: as of now (there are some issues with the approach sketched) no. 
This is intended as a simplified example of the pipeline of predicting. 
Probably one has to make folds & do cross-validation. 

```{r}

library(tidyverse)
## getting rid of shuffle because it is shit 
crqa_split_noshuf <- crqa_split %>%
  filter(resp1S.reality_status != "shuffled")


## 75% of the sample size
smp_size <- floor(0.75 * nrow(crqa_split_noshuf))

## set the seed to make your partition reproducible
set.seed(123)
train_ind <- sample(seq_len(nrow(crqa_split_noshuf)), size = smp_size)

## the above is not taking into account that we would like the diff. conditions / baselines to be equal in training and test - so this is just sample code. 

train <- crqa_split_noshuf[train_ind, ]
test <- crqa_split_noshuf[-train_ind, ]

## Building models 
library(pacman)
p_load(tidyverse, lme4)

## rescaling should be done. 
model1 = lm(hr1S.DET ~ resp1S.RR + resp1S.DET + resp1S.NRLINE + resp1S.maxL + resp1S.L + resp1S.ENTR + resp1S.rENTR + resp1S.LAM + resp1S.TT + (1|resp1S.condition) + (1|resp1S.reality_status),  data = train, REML = FALSE)
summary(model1)

## prediction 
test$pred <- predict(model1, test, allow.new.levels = TRUE)

## predictions visualized 
ggplot(test, aes(hr1S.DET, pred), color = ) +
  geom_point() +
  geom_smooth()

#### cross-validation would be better ####

```

