---
title: "A4_P1_function"
author: "JK"
date: "8 listopadu 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(pacman)
p_load(tidyverse,
       gridExtra, #grid.arrange()
       crqa, #crqa()
       lmerTest,
       doParallel, #parallel processing
       reshape2,
       Hmisc, #errorbars in plotting
       groupdata2) #downsampling

# parallel processing
cl <- makeCluster(detectCores(), type='PSOCK')
registerDoParallel(cl)
```

# PREPROCESSING
## LOADING CSV FILES

```{r data loading}
### list of file names to load
files <- list.files(path = "data/", pattern="Study3", full.names = T)


### loading funciton
read_heart <- function(filename) {
    raw <- read_csv(filename,
                    #reading columns, correct types, exculding ECG
                    col_types = list(time = col_double(),
                                     Resp1 = col_double(),
                                     Resp2 = col_double(),
                                     ECG1 = col_skip(),
                                     ECG2 = col_skip(),
                                     ReadingStart = col_integer(),
                                     ReadingStop = col_integer(),
                                     HR1 = col_double(),
                                     HR2 = col_double()))
    # make filename a vector
    name <- as.character(filename)
    # include filename as column
    data <- cbind(raw, name) %>%
      mutate(nrow = nrow(raw))
    
    # gather information from filename
    data <- data %>%
      #erase path details
      mutate(name = str_remove_all(name, "data/"),
         name = str_remove_all(name, ".csv")) %>%
      
      #create new variables from parts of the filename
      #filenames do not have same lengths, str_remove_all is for cleaning the leftovers resulting from this
      mutate(study = substr(name, 6, 6),
         # group
         group = substr(name, 9, 10),
         group = str_remove_all(group, "_"),
         # t
         t = substr(name, 12, 13),
         t = str_remove_all(t, "_"),
         t = str_remove_all(t, "T"),
         # condition
         condition = substr(name, 14, 30),
         condition = str_remove_all(condition, "_")) %>%
      
      select(-name)
    
    return(data)
}


### loop over the function
all <- map_df(files, read_heart) %>%
  # take study 3 only
  filter(study == "3") %>%
  # set column types again, as map_df messes things up
  mutate(t = factor(t),
         condition = factor(condition),
         ReadingStart = as.numeric(ReadingStart),
         ReadingStop = as.numeric(ReadingStop),
         nrow = as.numeric(nrow),
         study = factor(study),
         group = factor(group)) %>%
  rownames_to_column()
```


## PREPROCESSING FUNCTION

```{r preprocessing}
### preprocessing function
# includes: downsampling, outlier removal and scaling

idiot1_idiot2_analysis <- function(data, threshold) {
  
  ## DOWNSAMPLING
  
  # summarise
  d1 <- data %>%
    group(n = 100, method = 'greedy') %>%
    dplyr::summarise(
      TimeMs = mean(TimeMs,na.rm=T),
      HR1 = mean(HR1,na.rm=T),
      HR2 = mean(HR2,na.rm=T),
      Resp1 = mean(Resp1,na.rm=T),
      Resp2 = mean(Resp2,na.rm=T),
      rowname = rowname[1]) #the index we use to put them back together 
  
  # collect
  d2 <- left_join(d1, data, by = "rowname") %>%
    select(-matches("\\.y"))
  
  
  
  ## OUTLIERS
  # funciton
  removeOuts <- function(ts,threshold){
    ts[ts > (mean(ts,na.rm=T) +
               (threshold*sd(ts,na.rm=T))) | 
         ts < (mean(ts,na.rm=T) -
                 (threshold*sd(ts,na.rm=T)))] = mean(ts,na.rm=T)
    return(ts)
  }
  
  # set threshold
  threshold=threshold
  
  # do the job
  d3 <- d2 %>%
    group_by(group, condition) %>%
    mutate(hr1  = removeOuts(HR1.x, threshold),
           hr2  = removeOuts(HR2.x, threshold),
           resp1 = removeOuts(Resp1.x, threshold),
           resp2 = removeOuts(Resp2.x, threshold))
  
  
  
  ## SCALING
  
  # function
  z_scale <- function(column){
    column_c <- (column - mean(column)) / sd(column)
  }
  
  # do the job
  d4 <- d3 %>%
    group_by(condition, group) %>%
    mutate(resp1S = z_scale(resp1),
           resp2S = z_scale(resp2),
           hr1S = z_scale(hr1),
           hr2S = z_scale(hr2))
  
  ## OUTPUT
  return(d4)
  
}

# run funciton & remove raw data
d4 <- idiot1_idiot2_analysis(all, threshold = 2.5)
rm(all)
```


## PLOTTING FUNCTION
to get to know the dataset

```{r plotting}
plotty <- function(data, group_nr){
  c1 <- data %>%
    filter(group == group_nr) %>%
    ggplot() +
    geom_line(aes(as.numeric(TimeMs.x), hr1S, color = "P1")) +
    geom_line(aes(as.numeric(TimeMs.x), hr2S, color = "P2")) +
    labs(x = "time in 100 ms", y = "HR") +
    theme(legend.position="bottom")
  
  # scaled RESP
  c2 <- data %>%
    filter(group == group_nr) %>%
    ggplot() +
    geom_line(aes(as.numeric(TimeMs.x), resp1S, color = "P1")) +
    geom_line(aes(as.numeric(TimeMs.x), resp2S, color = "P2")) +
    labs(x = "time in 100 ms", y = "RESP") +
    theme(legend.position="bottom")
  
  ## colected
  grid.arrange(c1, c2, ncol=2, top = "Plots of physiological data (HR, RESP, ECG) with downsampling, outlier removal & scaling", 
               bottom = paste0("Group ", group_nr))
  
}

plotty(d4, group_nr = "2")
```


# OPTIMIZING PARAMETERS
## SETUP OF optimizeParam()

```{r optimize setup}
## set parameters
par = list(lgM = 50, 
           steps = seq(1, 6, 1), 
           radiusspan = 100,
           radiussample = 40, 
           normalize = 0, 
           rescale = 0, #slide code = 0
           mindiagline = 2,
           minvertline = 2, 
           tw = 0, 
           whiteline = FALSE, 
           recpt = FALSE, 
           fnnpercent = 10, 
           typeami = "mindip")



## version of optimizeParam that returnt an error message if something goes wrong
# agruments: timeseries and parameters for optimizeParam() function

non_picky_optimizeParam <- function(TS1, TS2, parameters) {
  
  return(
    # try running the expression using specified arugments
    tryCatch(expr = (optimizeParam(TS1, TS2, parameters, min.rec = 3.5, max.rec = 4.5)),
             # when error / warning occurs, it saves the message as character
           error=function(e) as.character(e), warning=function(w) as.character(w))
    )
}



## THE FUNCTION
optimizeAlot_tidy <- function(df, group_nr, parameter_list) {
  
  # one group only
  data <- df %>%
    dplyr::filter(group == as.character(group_nr))
  
  ## optimize
  
  HR <- non_picky_optimizeParam(data$hr1S, data$hr2S, parameters = parameter_list)
  
  RESP <- non_picky_optimizeParam(data$resp1S, data$resp2S, parameters = parameter_list)
  
  ## initialize dataframe
  
  bind_empty <- data_frame(radius=character(),
                           delay=character(), 
                           emddim=character(), 
                           group=character(),
                           metric=character()) 
  
  ## bind that
  
  bind_HR <- bind_empty %>%
    add_row(radius = as.character(ifelse(is_character(HR), HR[[1]], HR[["radius"]])),
           delay = as.character(ifelse(is_character(HR), HR[[1]], HR[["delay"]])),
           emddim = as.character(ifelse(is_character(HR), HR[[1]], HR[["emddim"]])),
           group = as.character(group_nr),
           metric = as.character("HR"))
  
  bind_RESP <- bind_empty %>%
    add_row(radius = as.character(ifelse(is_character(RESP), RESP[[1]], RESP[["radius"]])),
           delay = as.character(ifelse(is_character(RESP), RESP[[1]], RESP[["delay"]])),
           emddim = as.character(ifelse(is_character(RESP), RESP[[1]], RESP[["emddim"]])),
           group = as.character(group_nr),
           metric = as.character("RESP"))
  
  bind <- full_join(bind_HR, bind_RESP)
  
  ## return
  return(bind)
  
}
```

## running optimisation
watch out! Takes quite a while to run
```{r optimize run}
set.seed(666)
all_groups <- c(1, 2, 4:10)

system.time(optimal_para <- map_df(all_groups, 
                       optimizeAlot_tidy, 
                       df = d4,
                       parameter_list = par))

```


## median parameters
```{r med_optimal}
# taking median parameter from each metric to represent them all
med_optimal_para <- optimal_para %>%
  mutate(delay = as.numeric(delay),
         emddim = as.numeric(emddim),
         radius = as.numeric(radius)) %>%
  
  group_by(metric) %>%
  
  summarise(delay = median(delay, na.rm = T),
            emddim = median(emddim, na.rm = T),
            radius = median(radius, na.rm = T))
```


# CRQA
## SETTING UP FUNCTION FOR REAL PAIRS

```{r crqa function}
crqa_real <- function(df, group_nr_cond, var1, var2, del, emb, rad) {
  
  # filtering argument
  filtering_args <- data.frame(whack = group_nr_cond) %>%
    separate(whack, c("cond", "group_nr"), sep = "_")
  
  cond <- filtering_args$cond
  group_nr <- filtering_args$group_nr
  
  # filtering
  data <- df %>%
    dplyr::filter(condition == as.character(cond)) %>%
    dplyr::filter(group ==as.numeric(group_nr))
    
  
  # computing
  crqa_list <- list(crqa(ts1 = data[[as.character(var1)]], 
                            ts2 = data[[as.character(var2)]], 
                            delay = del, #delay 
                            embed = emb, #emdim 
                            radius = rad, #radius
                            normalize = 0,
                            rescale = 0,
                            mindiagline = 2,
                            minvertline = 2))
  
  # unlist
  crqa_unlist <- unlist(crqa_list)
  crqa_unlist$metric <- var1
  crqa_unlist$group <- group_nr
  crqa_unlist$condition <- cond
  crqa_unlist$radius <- rad
  
  # remove tyrant
  crqa_unlist$RP <- NULL

  # return
  crqa_df <- data.frame(crqa_unlist)
  return(crqa_df)
}
```


## running CRQA on real pairs
```{r crqa real}
set.seed(666) 
group_sync <- paste0("Synchronous_", c(1, 2, 4:10))
group_conv <- paste0("Conversation_", c(1, 2, 4:10))
group_turn <- paste0("TurnTaking_", c(1, 2, 4:10))

# loop trough all groups
real_sync_RESP <- map_df(group_sync,
                  crqa_real, 
                  df = d4,
                  var1 = "resp1S",
                  var2 = "resp2S",
                  del = 22.5,
                  emb = 2,
                  rad = 0.4078281)

real_conv_RESP <- map_df(group_conv,
                  crqa_real, 
                  df = d4,
                  var1 = "resp1S",
                  var2 = "resp2S",
                  del = 22.5,
                  emb = 2,
                  rad = 0.4078281)

real_turn_RESP <- map_df(group_turn,
                  crqa_real, 
                  df = d4,
                  var1 = "resp1S",
                  var2 = "resp2S",
                  del = 22.5,
                  emb = 2,
                  rad = 0.4078281)

###

real_sync_HR <- map_df(group_sync,
                  crqa_real, 
                  df = d4,
                  var1 = "hr1S",
                  var2 = "hr2S",
                  del = 10,
                  emb = 16,
                  rad = 1.4586380)

real_conv_HR <- map_df(group_conv,
                  crqa_real, 
                  df = d4,
                  var1 = "hr1S",
                  var2 = "hr2S",
                  del = 10,
                  emb = 16,
                  rad = 1.4586380)

real_turn_HR <- map_df(group_turn,
                  crqa_real, 
                  df = d4,
                  var1 = "hr1S",
                  var2 = "hr2S",
                  del = 10,
                  emb = 16,
                  rad = 1.4586380)
```

## merging output from real pairs
```{r}
Pattern_real <- grep("real_",names(.GlobalEnv),value=TRUE)

crqa_real <- list(real_conv_HR,
                   real_conv_RESP,
                   real_sync_HR,
                   real_sync_RESP, 
                   real_turn_HR,
                   real_turn_RESP) %>% reduce(full_join)
```


## SHUFFLED PAIRS
### shuffling
```{r shuffling}
set.seed(666)
d4_shuffle <- d4 %>% 
  mutate(
    hr1S = sample(hr1S),
    hr2S = sample(hr2S),
    resp1S = sample(resp1S),
    resp2S = sample(resp2S))

```

## running CRQA on shuffled paris
```{r crqa shuffled}
set.seed(666)
group_sync <- paste0("Synchronous_", c(1, 2, 4:10))
group_conv <- paste0("Conversation_", c(1, 2, 4:10))
group_turn <- paste0("TurnTaking_", c(1, 2, 4:10))

# loop trough all groups
shuff_sync_RESP <- map_df(group_sync,
                  crqa_real, 
                  df = d4_shuffle,
                  var1 = "resp1S",
                  var2 = "resp2S",
                  del = 22.5,
                  emb = 2,
                  rad = 0.4078281)

shuff_conv_RESP <- map_df(group_conv,
                  crqa_real, 
                  df = d4_shuffle,
                  var1 = "resp1S",
                  var2 = "resp2S",
                  del = 22.5,
                  emb = 2,
                  rad = 0.4078281)

shuff_turn_RESP <- map_df(group_turn,
                  crqa_real, 
                  df = d4_shuffle,
                  var1 = "resp1S",
                  var2 = "resp2S",
                  del = 22.5,
                  emb = 2,
                  rad = 0.4078281)

###

shuff_sync_HR <- map_df(group_sync,
                  crqa_real, 
                  df = d4_shuffle,
                  var1 = "hr1S",
                  var2 = "hr2S",
                  del = 10,
                  emb = 16,
                  rad = 1.4586380)

shuff_conv_HR <- map_df(group_conv,
                  crqa_real, 
                  df = d4_shuffle,
                  var1 = "hr1S",
                  var2 = "hr2S",
                  del = 10,
                  emb = 16,
                  rad = 1.4586380)

shuff_turn_HR <- map_df(group_turn,
                  crqa_real, 
                  df = d4_shuffle,
                  var1 = "hr1S",
                  var2 = "hr2S",
                  del = 10,
                  emb = 16,
                  rad = 1.4586380)
```


## merge output from shuffled pairs
```{r crqa shuffle}
Pattern_shuff <- grep("shuff_",names(.GlobalEnv),value=TRUE)

crqa_shuff <- list(shuff_conv_HR,
                   shuff_conv_RESP,
                   shuff_sync_HR,
                   shuff_sync_RESP, 
                   shuff_turn_HR,
                   shuff_turn_RESP) %>% reduce(full_join)
```


## SURROGARE
```{r crqa surrogate wrangle}
d5 <- d4 %>%
  dplyr::mutate(group2 = ifelse(group == 10, 3, group)) 
# This works because 2 comes after (just like 10 does. So, it works by accident - which is good enough for now.)
# WATCH OUT, MY WORKS WITH 3, SOME WORK WITH 2

d5$group2 <- as.factor(d5$group2)

#Subset for melting with RESP
d6 <- d5 %>%
  ungroup() %>%
  select(resp1S, resp2S, group2)

d7 <- melt(d6, id.vars = "group2")

#Subset for melting with HR
d8 <- d5 %>%
  ungroup() %>%
  select(hr1S, hr2S, group2)

d9 <- melt(d8, id.vars = "group2")

#Renaming both d7 & d9 
d7 <- d7 %>%
  rename(resp = variable, resp_value = value)

d9 <- d9 %>%
  rename(hr = variable, hr_value = value)

#combining & eliminating 
d10 <- cbind(d7, d9)
d10 <- d10[,-4] #getting rid of one of the group2 columns. 

#Adding a unique column 
d11 <- d10 %>%
  mutate(greatness = paste(group2, resp))

d11$greatness <- as.factor(as.numeric(as.factor(d11$greatness)))
#summary(d11$greatness) #great stuff. 

#adding something more 
#doing something 
d12 <- d5 %>%
  ungroup() %>%
  select(hr1S, hr2S, condition)

d13 <- melt(d12, id.vars = "condition")

d14 <- cbind(d11, d13)
d14 <- d14[,-c(8:9)]
d14$greatness <- as.numeric(d14$greatness)
```

```{r expand grid}
set.seed(666)
expand <- expand.grid(persons1 = seq(1,18,1), persons2 = seq(1,18,1)) %>%
  filter(persons1 < persons2)
  
#153 combinations. 
expand <- expand %>%
  rename(p1 = persons1, p2 = persons2) 
```

```{r surrogate function}
surrogate_RESP <- function(data, condition_name) {
  
  #create an empty df
  df <- data.frame()
  df <- setNames(data.frame(matrix(ncol=12, nrow=153)),c('p1','p2',"RR","DET","NRLINE","maxL","L","ENTR", "rENTR", "LAM", "TT", "metric"))
  
  
  
  for (n in 1:153) {
    # participants
    p1 <- dplyr::filter(data, data$greatness == expand[n,1], 
                        data$condition == as.character(condition_name))
    p2 <- dplyr::filter(data, data$greatness == expand[n,2], 
                        data$condition == as.character(condition_name))
    
    #vectors 
    v1 <- p1[["resp_value"]]
    v2 <- p2[["resp_value"]]
    
    #run crqa
    results <- crqa(v1, v2, embed = 2, delay = 25.5, radius = 0.408, normalize = 0,  rescale = 0,  mindiagline = 2,  minvertline = 2,  tw = 0,  whiteline = FALSE,  recpt = FALSE)
    
    # save into a df
    df$p1[n] <- unique(p1$greatness)
    df$p2[n] <- unique(p2$greatness)
    df$RR[n] <- results$RR
    df$DET[n] <- results$DET
    df$NRLINE[n] <- results$NRLINE
    df$maxL[n] <- results$maxL
    df$L[n] <- results$L
    df$ENTR[n] <- results$ENTR
    df$rENTR[n] <- results$rENTR
    df$LAM[n] <- results$LAM
    df$TT[n] <- results$TT
    df$metric <- "resp1S"
    df$condition <- condition_name
    df$radius <- 0.408
    
    n = n+1
  }
  return(df)    
}
###
surrogate_HR <- function(data, condition_name) {
  
  #create an empty df
  df <- data.frame()
  df <- setNames(data.frame(matrix(ncol=12, nrow=153)),c('p1','p2',"RR","DET","NRLINE","maxL","L","ENTR", "rENTR", "LAM", "TT", "metric"))
  
  
  
  for (n in 1:153) {
    # participants
    p1 <- dplyr::filter(data, data$greatness == expand[n,1], 
                        data$condition == as.character(condition_name))
    p2 <- dplyr::filter(data, data$greatness == expand[n,2], 
                        data$condition == as.character(condition_name))
    
    #vectors 
    v1 <- p1[["hr_value"]]
    v2 <- p2[["hr_value"]]
    
    #run crqa
    results <- crqa(v1, v2, embed = 16, delay = 10, radius = 1.459, normalize = 0,  rescale = 0,  mindiagline = 2,  minvertline = 2,  tw = 0,  whiteline = FALSE,  recpt = FALSE)
    
    # save into a df
    df$p1[n] <- unique(p1$greatness)
    df$p2[n] <- unique(p2$greatness)
    df$RR[n] <- results$RR
    df$DET[n] <- results$DET
    df$NRLINE[n] <- results$NRLINE
    df$maxL[n] <- results$maxL
    df$L[n] <- results$L
    df$ENTR[n] <- results$ENTR
    df$rENTR[n] <- results$rENTR
    df$LAM[n] <- results$LAM
    df$TT[n] <- results$TT
    df$metric <- "hr1S"
    df$condition <- condition_name
    df$radius <- 1.459
      
      n = n+1
  }
  return(df)    
}
```

```{r surrogate run}
set.seed(666)
condition_list <- names(table(d14$condition))

n = 1
surr_HR_df <- map_df(condition_list,
                     surrogate_HR,
                     data = d14)
n = 1
surr_RESP_df <- map_df(condition_list,
                       surrogate_RESP,
                       data = d14)

surr_r <- full_join(surr_HR_df, surr_RESP_df)
```
